Bayesian multi-proxy reconstruction of early Eocene latitudinal temperature gradients

### 2023-06-01 manuscript/main.qmd
CC BY licence in acknowledgements
add zenodo link

The authors are grateful to all those who have enabled this work by collecting, measuring, collating and screening geochemical and fossil data. The contribution of L.A.J. was supported by a Juan de la Cierva-formación 2021 fellowship (FJC2021-046695-I/MCIN/AEI/10.13039/501100011033) from the European Union "NextGenerationEU"/PRTR. 
<!-- regarding funding acknowledgement, I talked to my boss and he says I don't need to credit my funding as I have done this work largely in my spare time -->

@@

The data and code used to produce the results of this study are available via GitHub (<https://github.com/KEichenseer/PalaeoClimateGradient>) and the linked Zenodo repository (XXX).

>>>>

The authors are grateful to all those who have enabled this work by collecting, measuring, collating and screening geochemical and fossil data. The contribution of L.A.J. was supported by a Juan de la Cierva-formación 2021 fellowship (FJC2021-046695-I/MCIN/AEI/10.13039/501100011033) from the European Union "NextGenerationEU"/PRTR. For the purpose of open access, the authors have applied a Creative Commons Attribution (CC BY) licence to any Author Accepted Manuscript version arising from this submission.
<!-- regarding funding acknowledgement, I talked to my boss and he says I don't need to credit my funding as I have done this work largely in my spare time -->

@@

The data and code used to produce the results of this study are available via GitHub (<https://github.com/KEichenseer/PalaeoClimateGradient>) and the linked Zenodo repository (<https://zenodo.org/record/7995969>).
